### 2019-12-18 r/4_modelisation.Rmd

---
title: "4_modelisation"
author: "Psqrt"
date: "16/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages et fonctions externes

```{r, message=F, warning=F}
source("./0_packages.R")
```

```{r}
type_col = readRDS("./../data/type_col.rds")
train = data.table::fread(file = "./../data/train.csv", colClasses = type_col) %>% as.data.frame()
test = data.table::fread(file = "./../data/test.csv", colClasses = type_col) %>% as.data.frame()
```