### 2020-01-05 r/6_model_tuning.Rmd

---
title: "6_model_tuning"
author: "Psqrt"
date: "23/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages et fonctions externes

```{r, message=F, warning=F}
source("./0_packages.R")

# library(doMC)
# registerDoMC(cores = 8)
```

## Importations

```{r}
load("./../data/bases_29features.RData")

train_id = train$id
train_X = train %>% select(-id, -target)
train_Y = train$target
train_XY = train %>% select(-id)

test_id = test$id
test_X = test %>% select(-id, -target)
test_Y = test$target %>% as.numeric()
test_Y = test_Y - 1
```

## Exportations

Repertoire qui contiendra les sauvegardes de modèles.

```{r}
path_exportation = file.path("/media/psqrt/SquareX/SAVE_MODELS/save_2020")
path_exportation = file.path("/media/psqrt/DATA/save_models_2020")
```

## paramètres de validation

Stratégie de validation : 5 folds CV.

```{r}
tune_control <- trainControl(method = "cv", 
                             number = 5, 
                             summaryFunction = giniSummary, 
                             classProbs = T, 
                             savePredictions = T, 
                             verboseIter = T, 
                             sampling = "none") # none, smote, down, up
```

### Arbre de décision

```{r}

set.seed(1234)
modelLookup("rpart2")

tune_grid = expand.grid(
    maxdepth = 1:5
)

tree_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "rpart2"
)

save(tree_model, file = file.path(path_exportation, "tree_model.RData"))
rm(tree_model)
gc()

```

### Régression logistique

```{r}

set.seed(1234)
modelLookup("glm")

glm_binomial_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    method = "glm",
    family = "binomial"
)

save(glm_binomial_model, file = file.path(path_exportation, "glm_binomial_model.RData"))
rm(glm_binomial_model)
gc()

```

### Forêt aléatoire (ranger)

```{r}

set.seed(1234)
modelLookup("ranger")

tune_grid = expand.grid(
    mtry = c(3:(floor((ncol(train_XY)) * 0.8))),
    splitrule = "gini",
    min.node.size = 1
)

foret_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "ranger",
    importance = "impurity"
)

save(foret_model, file = file.path(path_exportation, "foret_model.RData"))
rm(foret_model)
gc()

```

### AdaBoosting

```{r}

set.seed(1234)
modelLookup("ada")

tune_grid = expand.grid(
    iter = 500,
    maxdepth = 5,
    nu = 0.1
)

ada_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "ada",
)

save(ada_model, file = file.path(path_exportation, "ada_model.RData"))
rm(ada_model)
gc()

```

### GLMnet

```{r}

set.seed(1234)
modelLookup("glmnet")

tune_grid = expand.grid(
    alpha = seq(0, 1, 0.1),
    lambda = seq(0, 3, 0.2)
)

glmnet_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "glmnet",
)

save(glmnet_model, file = file.path(path_exportation, "glmnet_model.RData"))
rm(glmnet_model)
gc()

```

### KNN

```{r}

set.seed(1234)
modelLookup("knn")

tune_grid = expand.grid(
    k = 3
)

kppv_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "knn",
)

save(kppv_model, file = file.path(path_exportation, "kppv_model.RData"))
rm(kppv_model)
gc()

```

### LDA

```{r}

set.seed(1234)
modelLookup("lda")

lda_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    method = "lda",
)

save(lda_model, file = file.path(path_exportation, "lda_model.RData"))
rm(lda_model)
gc()

```

### Gradient boosting

```{r}

set.seed(1234)
modelLookup("gbm")

tune_grid = expand.grid(
    n.trees = seq(300, 600, 100),
    interaction.depth = seq(1, 6, 1),
    shrinkage = 0.1,
    n.minobsinnode = 1
)

gbm_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "gbm"
)

save(gbm_model, file = file.path(path_exportation, "gbm_model.RData"))
rm(gbm_model)
gc()

```

### SVM (radial kernel)

```{r}

set.seed(1234)
modelLookup("svmRadial")

tune_grid = expand.grid(
    sigma = 1,
    C = 1
)

svm_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "svmRadial",
)

save(svm_model, file = file.path(path_exportation, "svm_model.RData"))
rm(svm_model)
gc()

```

### XGBoosting

```{r}

set.seed(1234)
modelLookup("xgbTree")

tune_grid = expand.grid(
    nrounds = seq(100, 500, 100),
    eta = c(0.05, 0.1),
    max_depth = c(4, 5, 6),
    gamma = 0,
    colsample_bytree = 0.7,
    min_child_weight = 0,
    subsample = 0.7
)

xgbtree_model = train(
    target ~ .,
    data = train_XY,
    metric = "NormalizedGini",
    trControl = tune_control,
    tuneGrid = tune_grid,
    method = "xgbTree",
)

save(xgbtree_model, file = file.path(path_exportation, "xgbtree_model.RData"))
rm(xgbtree_model)
gc()

```

### LGBM

```{r}
# LGBM
train_X_lgb  = train %>% 
    select(-id, -target) %>% 
    lgb.prepare() %>% 
    as.matrix()

train_Y_lgb = train %>% 
    select(target) %>% 
    lgb.prepare() %>% 
    as.matrix() - 1

train_Y_num = as.numeric(train$target) - 1

test_X_lgb   = test %>% 
    select(-id, -target) %>% 
    lgb.prepare() %>% 
    as.matrix()

test_Y_lgb = test %>% 
    select(target) %>% 
    lgb.prepare() %>% 
    as.matrix()

test_Y_num = as.numeric(test$target) - 1

train_XY_lgb = lgb.Dataset(train_X_lgb, label = train_Y_lgb)
```

#### Up

```{r, eval = F}
set.seed(1234)
params_lgb = list(
    objective        = "binary", # type of exercise
    metric           = "auc",    # metric to be evaluated
    learning_rate    = 0.01,     # shrinkage rate
    max_depth        = 10,       # max depth for tree model (used to deal with over-fitting when data is small)
    num_leaves       = 20,       # max number of leaves (nodes) in one tree
    # is_unbalance     = T,        # is data unbalanced (disable this if using scale_pos_weight)
    scale_pos_weight = 26,       # multiplication applied to every positive label weight (default: 1)
    min_data_in_leaf = 1,        # min number of data in one leaf (used to deal with over-fitting)
    feature_fraction = 0.8,      # randomly select part of the features on each iteration
    bagging_fraction = 0.8,      # randomly select part of the data without resampling
    bagging_freq     = 5,        # if != 0, enables bagging, performs bagging at every k iteration
    num_threads      = 6         # number of cpu cores (not threads) to use
)

up_lgb_cv = lgb.cv(
    params                = params_lgb,         # hyperparameters
    data                  = train_XY_lgb,       # lgb.Dataset object for training
    eval                  = lgb.normalizedgini, # custom metric, additionnal to first metric
    nrounds               = 1000,               # maximum iterations
    early_stopping_rounds = 50,                 # if metric evaluation doesn't increase
    verbose               = 1,                  # enable verbose
    eval_freq             = 50,                 # verbose every n iterations
    nfold                 = 5                   # k-folds CV
)

up_lgb_model <- lgb.train(
    params    = params_lgb,                        # hyperparameters
    data      = train_XY_lgb,                      # lgb.Dataset object for training
    valids    = list(train = train_XY_lgb),        # lgb.Dataset object for validation
    eval      = lgb.normalizedgini,                # custom metric, additionnal to first metric
    nrounds   = up_lgb_cv$best_iter, # nrounds from CV
    verbose   = 1,                                 # enable verbose
    eval_freq = 50                                 # verbose every n iterations
)
```

```{r}
# save(up_lgb_cv, file = "./../data/up_lgb_cv.RData")
# lgb.save(up_lgb_model, filename = "./../data/up_lgb_model.txt")
load("./../data/up_lgb_cv.RData")
up_lgb_model = lgb.load("./../data/up_lgb_model.txt")
```

```{r}
up_lgb_train_preds          = predict(up_lgb_model, train_X_lgb)
up_lgb_test_preds           = predict(up_lgb_model, test_X_lgb)
up_lgb_train_ngini          = normalizedGini(train_Y_num, up_lgb_train_preds)
up_lgb_test_ngini           = normalizedGini(test_Y_num, up_lgb_test_preds)
ngini_valid = up_lgb_cv[["record_evals"]][["valid"]][["Norm-gini"]][["eval"]] %>% unlist %>% max
c("Normalized Gini Coeff. (Train)"        = up_lgb_train_ngini,
  "Normalized Gini Coeff. (Valid - 5fCV)" = ngini_valid,
  "Normalized Gini Coeff. (Test)"         = up_lgb_test_ngini)
```

#### None

```{r, eval = F}
none_lgb_tune_df = data.frame(
    "max_depth" = numeric(),
    "num_leaves" = numeric(),
    "feature_fraction" = numeric(),
    "bagging_fraction" = numeric(),
    "validation" = numeric()
)

for (max_depth_param in c(5, 10, 15)){
    for (num_leaves_param in c(15, 20, 25)) {
        for (feature_fraction_param in c(0.7, 0.8)) {
            for (bagging_fraction_param in c(0.7, 0.8)) {

                set.seed(1234)
                params_lgb = list(
                    objective        = "binary",               # type of exercise
                    metric           = "auc",                  # metric to be evaluated
                    learning_rate    = 0.01,                   # shrinkage rate
                    max_depth        = max_depth_param,        # max depth for tree model (used to deal with over-fitting)
                    num_leaves       = num_leaves_param,       # max number of leaves (nodes) in one tree
                    is_unbalance     = T,                      # is data unbalanced (disable this if using scale_pos_weight)
                    min_data_in_leaf = 1,                      # min number of data in one leaf (used to deal with over-fitting)
                    feature_fraction = feature_fraction_param, # randomly select part of the features per iteration
                    bagging_fraction = bagging_fraction_param, # randomly select part of the data without resampling
                    bagging_freq     = 5,                      # if != 0, enables bagging, performs bagging at every k iteration
                    num_threads      = 6                       # number of cpu cores (not threads) to use
                )

                none_lgb_cv = lgb.cv(
                    params                = params_lgb,         # hyperparameters
                    data                  = train_XY_lgb,       # lgb.Dataset object for training
                    eval                  = lgb.normalizedgini, # custom metric, additionnal to first metric
                    nrounds               = 1000,               # maximum iterations
                    early_stopping_rounds = 50,                 # if metric evaluation doesn't increase
                    verbose               = 1,                  # enable verbose
                    eval_freq             = 50,                 # verbose every n iterations
                    nfold                 = 5                   # k-folds CV
                )

                row_param = data.frame(
                    "max_depth" = max_depth_param,
                    "num_leaves" = num_leaves_param,
                    "feature_fraction" = feature_fraction_param,
                    "bagging_fraction" = bagging_fraction_param,
                    "validation" = none_lgb_cv[["record_evals"]][["valid"]][["Norm-gini"]][["eval"]] %>% unlist %>% max
                )
                none_lgb_tune_df = none_lgb_tune_df %>% bind_rows(row_param)

            }
        }
    }
}

none_lgb_tune_df
# none_lgb_model <- lgb.train(
#   params    = params_lgb,                        # hyperparameters
#   data      = train_XY_lgb,                      # lgb.Dataset object for training
#   valids    = list(train = train_XY_lgb),        # lgb.Dataset object for validation
#   eval      = lgb.normalizedgini,                # custom metric, additionnal to first metric
#   nrounds   = none_lgb_cv$best_iter, # nrounds from CV
#   verbose   = 1,                                 # enable verbose
#   eval_freq = 50                                 # verbose every n iterations
# )
```

```{r}
# save(none_lgb_cv, file = "./../data/none_lgb_cv.RData")
# lgb.save(none_lgb_model, filename = "./../data/none_lgb_model.txt")
# load("./../data/none_lgb_cv.RData")
# none_lgb_model = lgb.load("./../data/none_lgb_model.txt")
```

```{r}
none_lgb_train_preds          = predict(none_lgb_model, train_X_lgb)
none_lgb_test_preds           = predict(none_lgb_model, test_X_lgb)
none_lgb_train_ngini          = normalizedGini(train_Y_num, none_lgb_train_preds)
none_lgb_test_ngini           = normalizedGini(test_Y_num, none_lgb_test_preds)
ngini_valid = none_lgb_cv[["record_evals"]][["valid"]][["Norm-gini"]][["eval"]] %>% unlist %>% max
c("Normalized Gini Coeff. (Train)"        = none_lgb_train_ngini,
  "Normalized Gini Coeff. (Valid - 5fCV)" = ngini_valid,
  "Normalized Gini Coeff. (Test)"         = none_lgb_test_ngini)
```

<!-- ## stacking glm -->

<!-- ```{r} -->
<!-- # stacking_train = toto_rpart$df_recap %>% dplyr::select(rowIndex, target = obs, rpart_learner = pred) %>%  -->
<!-- #     left_join(toto_logistic$df_recap %>% dplyr::select(rowIndex, glm_learner = pred)) %>%  -->
<!-- #     left_join(toto_foret$df_recap %>% dplyr::select(rowIndex, rf_learner = pred)) %>%  -->
<!-- #     # left_join(toto_ada$df_recap %>% dplyr::select(rowIndex, ada_learner = pred)) %>%  -->
<!-- #     # left_join(toto_xgbtree$df_recap %>% dplyr::select(rowIndex, xgbtree_learner = pred)) %>%  -->
<!-- #     left_join(toto_glmnet$df_recap %>% dplyr::select(rowIndex, glmnet_learner = pred)) %>%  -->
<!-- #     left_join(toto_kppv$df_recap %>% dplyr::select(rowIndex, knn_learner = pred)) -->
<!-- #     # left_join(toto_lda$df_recap %>% dplyr::select(rowIndex, lda_learner = pred)) %>%  -->
<!-- #     # left_join(toto_gbm$df_recap %>% dplyr::select(rowIndex, gbm_learner = pred)) %>%  -->
<!-- #     # left_join(toto_svm_rad$df_recap %>% dplyr::select(rowIndex, svm_rad_learner = pred)) -->

<!-- pred_foret = predict(foret, train) -->
<!-- pred_glmnet = predict(elastic, train) -->
<!-- pred_kppv = predict(kppv, train) -->
<!-- pred_logistic = predict(logistic, train) -->
<!-- pred_rpart = predict(rpart, train) -->

<!-- save(pred_foret, pred_glmnet, pred_kppv, pred_logistic, pred_rpart, file = "./../output/preds.RData") -->

<!-- stacking_train = data.frame( -->
<!--     "id" = train$id, -->
<!--     "target" = train$target, -->
<!--     "foret_pred" = pred_foret, -->
<!--     "glmnet_pred" = pred_glmnet, -->
<!--     "kppv_pred" = pred_kppv, -->
<!--     "logistic_pred" = pred_logistic, -->
<!--     "rpart_pred" = pred_rpart -->
<!-- ) -->

<!-- stacking_glm = train( -->
<!--     target ~ . - id, -->
<!--     data = stacking_train, -->
<!--     metric = "ROC", -->
<!--     trControl = tune_control, -->
<!--     method = "glm", -->
<!--     family = "binomial" -->
<!-- ) -->

<!-- toto_stacking_glm = eval_model(stacking_glm, "yes", "no", T) -->

<!-- ################################################################################# -->

<!-- tune_grid = expand.grid( -->
<!--     mtry = c(1:(floor((ncol(stacking_train) - 2)))), -->
<!--     # splitrule = c("gini", "extratrees"), -->
<!--     splitrule = "gini", -->
<!--     min.node.size = 1 -->
<!-- ) -->

<!-- foret_stacking = train( -->
<!--     target ~ . - id, -->
<!--     data = stacking_train, -->
<!--     metric = "ROC", -->
<!--     trControl = tune_control, -->
<!--     tuneGrid = tune_grid, -->
<!--     method = "ranger", -->
<!--     importance = "impurity" -->
<!-- ) -->

<!-- toto_stacking_ranger = eval_model(foret_stacking, "yes", "no", T) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- tune_control_final <- trainControl(method = "none", -->
<!--                                    summaryFunction = twoClassSummary, # prSummary -->
<!--                                    classProbs = T, -->
<!--                                    savePredictions = T, -->
<!--                                    sampling = "smote") -->

<!-- final_stacking_glm = train( -->
<!--     target ~ . - id, -->
<!--     data = stacking_train, -->
<!--     metric = "ROC", -->
<!--     trControl = tune_control_final, -->
<!--     method = "glm", -->
<!--     family = "binomial" -->
<!-- ) -->

<!-- tune_grid_foret_stacking = expand.grid( -->
<!--     mtry = foret_stacking$bestTune$mtry, -->
<!--     splitrule = foret_stacking$bestTune$splitrule, -->
<!--     min.node.size = foret_stacking$bestTune$min.node.size -->
<!-- ) -->

<!-- final_stacking_ranger = train( -->
<!--     target ~ . - id, -->
<!--     data = stacking_train, -->
<!--     metric = "ROC", -->
<!--     trControl = tune_control_final, -->
<!--     tuneGrid = tune_grid_foret_stacking, -->
<!--     method = "ranger", -->
<!--     importance = "impurity" -->
<!-- ) -->

<!-- pred_foret_test = predict(foret, test) -->
<!-- pred_glmnet_test = predict(elastic, test) -->
<!-- pred_kppv_test = predict(kppv, test) -->
<!-- pred_logistic_test = predict(logistic, test) -->
<!-- pred_rpart_test = predict(rpart, test) -->

<!-- save(pred_foret_test, pred_glmnet_test, pred_kppv_test, pred_logistic_test, pred_rpart_test,  -->
<!--      file = "./../output/preds_test.RData") -->

<!-- load("./../output/preds_test.RData") -->

<!-- pred_foret_test = pred_foret_test %>% as.character() -->
<!-- pred_foret_test[pred_foret_test == "yes"] = "1" -->
<!-- pred_foret_test[pred_foret_test == "no"] = "0" -->
<!-- pred_foret_test = pred_foret_test %>% as.numeric() -->

<!-- target = test$target %>% as.character() -->
<!-- target[target == "yes"] = "1" -->
<!-- target[target == "no"] = "0" -->
<!-- target = target %>% as.numeric() -->

<!-- normalizedGini <- function(aa, pp) { -->
<!--     Gini <- function(a, p) { -->
<!--         if (length(a) !=  length(p)) stop("Actual and Predicted need to be equal lengths!") -->
<!--         temp.df <- data.frame(actual = a, pred = p, range=c(1:length(a))) -->
<!--         temp.df <- temp.df[order(-temp.df$pred, temp.df$range),] -->
<!--         population.delta <- 1 / length(a) -->
<!--         total.losses <- sum(a) -->
<!--         null.losses <- rep(population.delta, length(a)) # Hopefully is similar to accumulatedPopulationPercentageSum -->
<!--         accum.losses <- temp.df$actual / total.losses # Hopefully is similar to accumulatedLossPercentageSum -->
<!--         gini.sum <- cumsum(accum.losses - null.losses) # Not sure if this is having the same effect or not -->
<!--         sum(gini.sum) / length(a) -->
<!--     } -->
<!--     Gini(aa,pp) / Gini(aa,aa) -->
<!-- } -->

<!-- test_preds_yo = predict(elastic, test %>% select(-target), type = "prob")[,2] -->
<!-- normalizedGini(aa = target, pp = pred_foret_test) -->
<!-- MLmetrics::NormalizedGini(test_preds_yo, test$target) -->
<!-- MLmetrics::NormalizedGini(c(0, 0), c(0, 0)) -->

<!-- stacking_test = data.frame( -->
<!--     "id" = test$id, -->
<!--     "target" = test$target, -->
<!--     "foret_pred" = pred_foret_test, -->
<!--     "glmnet_pred" = pred_glmnet_test, -->
<!--     "kppv_pred" = pred_kppv_test, -->
<!--     "logistic_pred" = pred_logistic_test, -->
<!--     "rpart_pred" = pred_rpart_test -->
<!-- ) -->

<!-- # pred_stacking_test = predict(final_stacking_glm, stacking_test) -->

<!-- toto_stacking_glm_test = test_model(final_stacking_glm, stacking_test, "yes", "no", T) -->

<!-- toto_stacking_ranger_test = test_model(final_stacking_ranger, stacking_test, "yes", "no", T) -->

<!-- pred_stacking_test %>% table -->
<!-- table(pred_stacking_test, test$target) -->

<!-- ``` -->