### 2020-01-05 r/7_model_evaluation.Rmd

---
title: "7_model_evaluation"
author: "Psqrt"
date: "03/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages et fonctions externes

```{r, message=F, warning=F}
source("./0_packages.R")

library(doMC)
registerDoMC(cores = 1)
```

## Importations

```{r}
load("./../data/bases_29features.RData")

train_id = train$id
train_XY = train %>% select(-id)
train_X = train %>% select(-id, -target)
train_Y = train$target %>% as.numeric()
train_Y = train_Y - 1

test_id = test$id
test_X = test %>% select(-id, -target)
test_Y = test$target %>% as.numeric()
test_Y = test_Y - 1
```

## Zone de stockage

```{r}
path_exportation = file.path("/media/psqrt/SquareX/SAVE_MODELS/save_2020")
path_exportation = file.path("/media/psqrt/DATA/save_models_2020")
path_exportation = file.path("/home/psqrt/Téléchargements/000")
```

```{r, eval = F}
df_score_modeles = data.frame("Method" = character(),
                              "Sampling" = character(),
                              "Train" = numeric(),
                              "Validation" = numeric(),
                              "Test" = numeric(),
                              stringsAsFactors = F)
donnees_modeles = list.files(path_exportation)
donnees_modeles = donnees_modeles[-grep("ada", donnees_modeles)]
for (rdata_file in donnees_modeles){
    print(rdata_file)
    modele = gsub(".RData", "", rdata_file)
    print(modele)
    load(file.path(path_exportation, rdata_file))
    df_score_modeles = df_score_modeles %>%
        bind_rows(caret_eval_gini(get(modele), train_X, test_X, train_Y, test_Y))
    rm(list = get("modele"))
}
```

```{r}
load("./../data/df_score_modeles")

df_score_modeles %>% 
    filter(Method != "rpart2") %>% 
    ggplot() +
    aes(x = Sampling, y = Validation, group = Sampling, label = Method) +
    geom_hline(yintercept = 0.2721429, color = "red", linetype = 2) +
    stat_boxplot(geom = "errorbar", aes(color = Sampling)) +
    geom_boxplot(aes(color = Sampling)) +
    geom_point(aes(color = Method)) +
    geom_text_repel(direction = "x", nudge_x = -0.2) +
    coord_flip() +
    xlab("Sampling Strategy") +
    ylab("Normalized Gini Coefficient (5 folds CV)") +
    annotation_custom(grob = textGrob(label = "LGBM benchmark", gp = gpar(fontsize = 9, col = "red")), xmin = -3.5, ymin = 0.272) +
    theme_bw() +
    theme(legend.position = "none")
```